\section{Acknowledgments}
\label{sec:acknowledgments}

This research was made possible through the generous support and resources provided by the open-source community and academic institutions. We would like to express our gratitude to the following individuals and organizations:

\subsection{Institutional Support}

We acknowledge the support from the Department of Computer Science at our institution, which provided the computational resources necessary for conducting extensive benchmarking and validation experiments. The high-performance computing facilities enabled us to perform comprehensive evaluations across multiple hardware configurations and workload scenarios.

\subsection{Open-Source Community}

Our work builds upon the foundational contributions of the open-source community:

\begin{itemize}
    \item The AMDGPU driver developers for providing comprehensive hardware monitoring capabilities
    \item The OpenCL working group for establishing standards for heterogeneous computing
    \item The PyTorch and TensorFlow communities for deep learning frameworks and benchmarks
    \item The scientific Python ecosystem (NumPy, SciPy, scikit-learn) for numerical computing tools
    \item The LaTeX community for document preparation systems
\end{itemize}

\subsection{Technical Contributions}

Special thanks to the researchers and engineers who have contributed to the development of energy-efficient computing techniques:

\begin{itemize}
    \item Contributors to matrix multiplication algorithm research, particularly in the areas of low-rank approximation and fast algorithms
    \item Developers of power monitoring and profiling tools for GPU architectures
    \item Researchers in machine learning for algorithm selection and optimization
    \item Engineers working on legacy hardware optimization and modernization
\end{itemize}

\subsection{Collaborators and Reviewers}

We are grateful to our colleagues who provided valuable feedback during the development process and manuscript preparation. Their insights helped refine our methodology and strengthen the experimental validation.

\subsection{Hardware Donations}

We acknowledge the contribution of hardware resources that enabled this research, including legacy GPU systems that formed the basis of our experimental platform.

\subsection{Funding Support}

This work was supported by internal research funding allocated for exploring energy-efficient computing solutions on legacy hardware platforms.

The authors would like to thank the anonymous reviewers for their constructive feedback, which helped improve the clarity and rigor of this work.

Finally, we dedicate this work to advancing sustainable computing practices that extend the useful life of existing hardware infrastructure while reducing the environmental impact of computational workloads.